MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
note random effects

<!-- ### Significant Covariates -->
<!-- Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates -->
<!-- ```{r preAdjusted.covariates, cache=TRUE} -->
<!-- # Find correlation between PC's of gene expression with covariates -->
<!-- preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E,  -->
<!--                                                  COVARIATES, -->
<!--                                                  'NULL design(voom-normalized)',  -->
<!--                                                  isKeyPlot=TRUE,  -->
<!--                                                  MIN_PVE_PCT_PC = 1) -->
<!-- ``` -->

<!-- Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars` -->
<!-- ```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12} -->
<!-- preAdjustedSigCovars[["PC_res"]][[2]]$plotData -->
<!-- ``` -->

### Model Identification
```{r fxn}
# Function to fit a mixed effect model and return BIC
fitMixedEffectModel <- function(varsToFit, random_effect, lcpm, covars, covars_to_fit){

}
```

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("Institution", "Reported_Gender", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("LibraryBatch", "FlowcellBatch")))
phase2
```

>>>>

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "Reported_Gender", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)")))
phase2
```
